Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2023-06-06 paper/ms.tex
Remove line numbers
Add Federico comments

We don't believe our method is the only nor even the best way to include gas.
One advantage of our method, though, is that it approximates the expectation
that in the bar region the gas surface density should be significantly reduced
\citep[e.g.][]{1993RPPh...56..173S}}

@@

After $5\,\textrm{Gyr}$, the $10\,\Msun/\textrm{pc}^2$ simulation has a gas
fraction of $5.7\%$, but still exhibits constant pattern speed behavior. As a
result, we conclude that for the disk, bar, and halo properties considered in
this work, a gas fraction of only approximately $5\%$ is necessary in order for
the proposed stabilizing mechanism to operate. {\bf We stress that this gas
fraction threshold is only for the system considered in this work. Systems with
different structural parameters may require a different threshold. For example,
\citet{2015MNRAS.454.3166A} find slowdown behavior in a barred disk $10$ times
less massive than ours with a gas fraction of $10\%$. To make things more
complicated, \citet{2010ApJ...719.1470V} find that the gas fraction cutoff
varies with the softening length used. Determining exactly how the gas fraction
cutoff varies with these considerations deserves further attention.}

@@

\citet{2013MNRAS.429.1949A, 2014MNRAS.438L..81A} find stable evolution in \Rot{}
for a triaxial halo over $10\,\textrm{Gyr}$ with initial (final) gas fractions
of $100\%$ ($7\%$), $75\%$ ($6\%$), and $50\%$ ($5\%$). For a model with $20\%$
($3\%$) gas fraction they find an increasing \Rot{}. In their model with a
spherical halo they always find increasing \Rot{}, contrary to the present work.
We note there is a structural difference in their dark matter halo. They use a
cored isothermal sphere as opposed to our Hernquist halo. It is not clear to us
the impact this would have on the expected torque from the halo (i.e., the
velocity structure of their halo may allow for more efficient capture and thus
stronger torquing). {\bf The bar locking process (or something similar) which we
propose in this paper is not mentioned by these authors.}

>>>>

We do not believe our method is the only nor even the best way to include gas.
One advantage of our method, though, is that it approximates the expectation
that in the bar region the gas surface density should be significantly reduced
\citep[e.g.][]{1993RPPh...56..173S}}

@@

After $5\,\textrm{Gyr}$, the $10\,\Msun/\textrm{pc}^2$ simulation has a gas
fraction of $5.7\%$, but still exhibits constant pattern speed behavior. As a
result, we conclude that for the disk, bar, and halo properties considered in
this work, a gas fraction of only approximately $5\%$ is necessary in order for
the proposed stabilizing mechanism to operate. {\bf We stress that this gas
fraction threshold is only for the system considered in this work. Systems with
different structural parameters may require a different threshold. For example,
\citet{2015MNRAS.454.3166A} find slowdown behavior in a barred disk $10$ times
less massive than ours with a gas fraction of $10\%$. To make things more
complicated, \citet{2010ApJ...719.1470V} find that the gas fraction cutoff
varies with the softening length used. Determining exactly how the gas fraction
cutoff varies with these properties deserves further attention.}

@@

\citet{2013MNRAS.429.1949A, 2014MNRAS.438L..81A} find stable evolution in \Rot{}
for a triaxial halo over $10\,\textrm{Gyr}$ with initial (final) gas fractions
of $100\%$ ($7\%$), $75\%$ ($6\%$), and $50\%$ ($5\%$). For a model with $20\%$
($3\%$) gas fraction they find an increasing \Rot{}. In their model with a
spherical halo they always find increasing \Rot{}, contrary to the present work.
We note there is a structural difference in their dark matter halo. They use a
cored isothermal sphere as opposed to our Hernquist halo. It is not clear to us
the impact this would have on the expected torque from the halo (i.e., the
velocity structure of their halo may allow for more efficient capture and thus
stronger torquing). {\bf The bar locking process (or a similar mechanism) that
we propose in this paper is not mentioned by these authors.}
